ESRC SDAI Application

### 2019-06-07 Draft.tex
update

@@

>>>>

anything that affects propensity to drink/financial stress

@@

\href{https://www.birminghammail.co.uk/news/midlands-news/universal-credit-rolled-out-across-14142901}{Universal credit roll-out in the West Midlands}

\href{https://www.birminghammail.co.uk/black-country/universal-credit-claimants-black-country-15946831}{Universal credit roll-out in the Black Country}

food bank dependence? data on housing e.g. evictions? homelessness.
